Kaggle-in-class Data Challenges can Boost Student Learning

### 2018-03-18 paper-kaggle.Rmd
More in the 'Participants' section

---
title: Kaggle-in-class Data Challenges can Boost Student Learning
# to produce blinded version set to 1
# blinded: 0
author: 
  - name: Julia Polak
    affiliation: Department of Statistics, University of Melbourne
  - name: Dianne Cook
    affiliation: Department of Econometrics and Business Statistics, Monash University
bibliography: bibliography.bib
link-citations: true
fig_caption: yes
keywords: technology, statistical modeling, data science, statistics education
#- that do not appear in the title
abstract: >
  Kaggle is a data modeling competition service, where participants compete to build a model with lower predictive error than other participants. Several years ago they released a reduced service that enables instructors to run competitions in a classroom setting. This paper describes the results of an experiment to determine if the participating in a predictive modeling competition enhances learning. The evidence suggests it does. In addition, students were surveyed to examine if the competition improved engagement and interest in the class.
output: rticles::asa_article
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(knitcitations)
library(RefManageR)
library("tidyverse")
#library("ggpubr")
library("readxl")
library("gridExtra")

@@

-	Time period: semester two 2016

-	MAST90083: 63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;

@@

@@

>>>>

---
title: Kaggle-in-class Data Challenges can Boost Student Learning
# to produce blinded version set to 1
# blinded: 0
author: 
  - name: Julia Polak
    affiliation: Department of Statistics, University of Melbourne
  - name: Dianne Cook
    affiliation: Department of Econometrics and Business Statistics, Monash University
bibliography: bibliography.bib
link-citations: true
fig_caption: yes
#keywords:
#- 3 to 6 keywords
#- that do not appear in the title
abstract: >
  The text of your abstract.  200 or fewer words.
output: rticles::asa_article
---

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(knitcitations)
library(RefManageR)
library("tidyverse")
library("ggpubr")
library("readxl")
library("gridExtra")

@@

-	Time period: semester two 2017

-	MAST90083:

63 enrolled students; postgraduate level; background: math & stats, IT and actuarial science;

Students were randomly assigned to one of two groups, regression (R) or classification (C). Each group will have a data competition designed for that topic, made available through kaggle in class (https://inclass.kaggle.com). Students wored individually to build predictive models, and submit predictions for the first 16 days. On the 16^{th} day of the competition students received an email that they allowed to establish groups and continue the competition as a group. The competition was continued for additional 7 days. In case they chose to form a group, the final score of the group in total was accounted as their individual mark towards the final grade for the subject and analysed in this project.  Only 3 groups were formed, two groups with 3 students and one group with two students. All other students chose to continue the competition individually.

Note that the data competition was compulsory to all the students. The volunteering part was the questionnaire at the end of the semester asking for feedback on aspects of the class such as their competition experience, their favourite topic of the semester, and their enjoyment of the material in the subject.

@@

## Used Platform

Kaggle in class (https://inclass.kaggle.com)...

@@

# Acknowledgments

This project (title: Effect of Data Competition on Learning Experience) has been approved by the Faculty of Science Human Ethics Advisory Group University of Melbourne (Ethics ID: 1749858.1 on September the 4th, 2017) and by XXX Ethics Advisory Group Monash University (Ethics ID: XXX on XXX, 2017).
